%!TEX root = ../lod-group1.tex
\section{Discussion of Evaluation Results}
\label{sec_discussion}

The results shown in Section \ref{sec_evaluation} give a lot of insight about the used approach.
The following section will discuss these findings and show conclusions and possible improvements.

The evaluation of increasing the candidate set size showed only an improvement to a certain point.
This allows the conclusion, that with the current candidate selection approach the correct movie is in most cases either already in the first movies or it will not be added anyway.
Surprisingly, the precision got even worse with a bigger candidate set.
That implies, that a better matching incorrect movie was found in bigger candidate sets.

Figure \ref{fig_baseline} shows the huge improvement of the discussed algorithm to the baseline approach.
This improvement can be traced back to the limiting factors of the baseline approach, which have already been explained in Section \ref{subsec_method_matching}.

On the other hand, Figure \ref{fig_baseline} also shows results for matching movies with no IMDb-ID annotated.
When comparing this with the results from movies, which have an IMDb-ID annotated, a bias is clearly visible.
Both, precision and recall are significantly lower.
This can be explained by the general lower annotation quality of those movies.
If movies do not have an IMDb-ID annotated, they have fewer data annotated in general.
Some movies even only have a name, with no further data.
As a consequence further parameter optimization should be done on movies without an IMDb-ID.
However, as no extensive gold standard exists for these movies, such an optimization was not possible in the scope of this paper.
Nonetheless, compared to the baseline approach it is still a good improvement.

Even though the results are already good there is still room for improvement.
The analysis of the wrongly matched movies and the matches which were not found, as listed in Section \ref{subsec_evaluation_matching}, has shown that the biggest possible gain lies in improving the way the candidates are selected.
Since candidate selection is based on the name and the year at the moment, movies with names that are not annotated so far are most likely not found.
Thus, further criterias should be considered when calculating the pre-score for selecting candidates.
This could also solve the problem described above, that an increased candidate set size does not yield better results, but in fact a worse precision.

Especially selecting a set of movies as candidates without looking at their name could help.
However, the movies that need to be matched, i.e. the one that do not have an IMDb-ID annotated, usually have very few other properties annotated.
Table \ref{table_properties} shows the data available for these movies.

\begin{table}[h]
\setlength{\tabcolsep}{.52em}
\def\arraystretch{1.0}
\begin{tabular}{c|c|c|c|c|c|c|c|c}
%\hline
overview & runtime & genre & \begin{tabular}[c]{@{}l@{}}prod.\\  country\end{tabular} & keywords & \begin{tabular}[c]{@{}l@{}}home\\  page\end{tabular} & \begin{tabular}[c]{@{}l@{}}prod.\\  company\end{tabular} & tagline & budget \\ \hline
74.20    & 47.10   & 40.36 & 23.81              & 13.72    & 13.29    & 12.44                                                           & 10.18   & 1.12  \\ %\hline
\end{tabular}
\caption{This shows available annotated information in movies without an IMDb-ID, that could be used for matching. All values in percent.}
\label{table_properties}
\end{table}

Possible further attributes to consider are overview (short plot summary), runtime and genre.
However, integrating them is not straightforward, as overview is an free text field, the runtime varies up to 10 minutes between data sources, and the genre is not very selective.
